---
title: 'HW10 : Web Scraping Script'
author: "Emre Yurtbay"
date: "4/1/2019"
output: pdf_document
---

## Web Scraping Description
To supplement our election related tweets, we also used web scraping to collect polling data from RealClearPolitics.com. We  gathered polling data from multiple states, including Florida, Georgia, Nevada, and Arizona, which totals to 1138 rows. There is no indication that we should not scrape the data, as it is public domain already. A good example of one of the webpages we scraped can be found here: "https://www.realclearpolitics.com/epolls/2018/governor/fl/florida_governor_desantis_vs_gillum-6518.html#polls." 

```{r}
library(XML)

# start the table with a file
url <- "https://www.realclearpolitics.com/epolls/2018/governor/fl/florida_governor_desantis_vs_gillum-6518.html#polls"
download.file(url, destfile = "/Users/emreyurtbay/Documents/Rice/junior/stat405/advfn.html")
doc <- htmlParse("/Users/emreyurtbay/Documents/Rice/junior/stat405/advfn.html")

# Fix names and free the doc
polling <- readHTMLTable(doc)[[4]][,c(2,5,6)]
colnames(polling) <-c("Date", "Democrat", "Republican")
polling
free(doc)

# URLS we want to scrape from
urls <- c(
        #"https://www.realclearpolitics.com/epolls/other/2018_generic_congressional_vote-6185.html#polls"
        "https://www.realclearpolitics.com/epolls/2018/governor/fl/florida_governor_desantis_vs_gillum-6518.html#polls",
        "https://www.realclearpolitics.com/epolls/2018/governor/ga/georgia_governor_kemp_vs_abrams-6628.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/ak/alaska_governor_dunleavy_vs_begich-6711.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/nv/nevada_governor_laxalt_vs_sisolak-6422.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/or/oregon_governor_buehler_vs_brown-6428.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/tx/texas_governor_abbott_vs_valdez-6435.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/nm/new_mexico_governor_pearce_vs_grisham-6440.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/ca/california_governor_cox_vs_newsom-6593.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/ny/new_york_governor_molinaro_vs_cuomo-6536.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/pa/pennsylvania_governor_wagner_vs_wolf-6542.html#polls",
        "https://www.realclearpolitics.com/epolls/2018/governor/oh/ohio_governor_dewine_vs_cordray-6426.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/nh/new_hampshire_governor_sununu_vs_kelly-6561.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/ma/massachusetts_governor_baker_vs_gonzalez-6418.html",
        "https://www.realclearpolitics.com/epolls/2018/governor/ct/connecticut_governor_stefanowski_vs_lamont-6577.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/fl/florida_senate_scott_vs_nelson-6246.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/ca/california_senate_feinstein_vs_de_leon-6592.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/tx/texas_senate_cruz_vs_orourke-6310.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/nm/new_mexico_senate_rich_vs_heinrich_vs_johnson-6663.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/az/arizona_senate_mcsally_vs_sinema-6328.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/nv/nevada_senate_heller_vs_rosen-6304.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/mt/montana_senate_rosendale_vs_tester-6306.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/mo/missouri_senate_hawley_vs_mccaskill-6280.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/tn/tennessee_senate_blackburn_vs_bredesen-6308.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/in/indiana_senate_braun_vs_donnelly_vs_brenton-6671.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/oh/ohio_senate_renacci_vs_brown-6331.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/mi/michigan_senate_james_vs_stabenow-6325.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/wi/wisconsin_senate_vukmir_vs_baldwin-6313.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/wv/west_virginia_senate_morrisey_vs_manchin-6258.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/va/virginia_senate_stewart_vs_kaine-6321.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/pa/pennsylvania_senate_barletta_vs_casey-6312.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/ny/new_york_senate_farley_vs_gillibrand-6539.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/ma/massachusetts_senate_diehl_vs_warren-6581.html",
        "https://www.realclearpolitics.com/epolls/2018/senate/ct/connecticut_senate_corey_vs_murphy-6262.html",
        "https://www.realclearpolitics.com/epolls/2016/president/us/general_election_trump_vs_clinton-5491.html"
         )

for (u in urls) {
  
  # download file
  download.file(u, destfile = "/Users/emreyurtbay/Documents/Rice/junior/stat405/advfn.html")
  doc <- htmlParse("/Users/emreyurtbay/Documents/Rice/junior/stat405/advfn.html")
  
  
  # Various tables we want to scrape
  if(length(readHTMLTable(doc)) > 2){
    temp <- readHTMLTable(doc)[[4]][,c(2,5,6)]
    colnames(temp) <-c("Date", "Democrat", "Republican")
    polling <- rbind(polling, temp)
  } 
  
  else if (length(readHTMLTable(doc)) > 1){
    temp <- readHTMLTable(doc)[[2]][,c(2,5,6)]
    colnames(temp) <-c("Date", "Democrat", "Republican")
    polling <- rbind(polling, temp)
    
  } else {
    temp <- readHTMLTable(doc)[[1]][,c(2,5,6)]
    colnames(temp) <-c("Date", "Democrat", "Republican")
    polling <- rbind(polling, temp)
  }
  
  free(doc)
  
}

# add a final url  
url <- "https://www.realclearpolitics.com/epolls/other/2018_generic_congressional_vote-6185.html"
download.file(url, destfile = "/Users/emreyurtbay/Documents/Rice/junior/stat405/advfn.html")
doc <- htmlParse("/Users/emreyurtbay/Documents/Rice/junior/stat405/advfn.html")
temp <- readHTMLTable(doc)[[4]][,c(2,4,5)]
colnames(temp) <-c("Date", "Democrat", "Republican")
polling <- rbind(polling, temp)
free(doc)
```


```{r}
nrow(polling)
```

```{r}
polling <- write.csv(polling, file = "/Users/emreyurtbay/Documents/Rice/junior/stat405/polling.csv")
```

```{r}
# Send to SQL DB
library(RSQLite)
dcon <- dbConnect(SQLite(),
                  dbname = "/Users/emreyurtbay/Documents/Rice/junior/stat405/group2.sqlite")
table <- read.csv(paste0("/Users/emreyurtbay/Documents/Rice/junior/stat405/polling.csv"))
dbWriteTable(conn = dcon, name = "polling-data", table,
             append = TRUE, row.names = FALSE)
```

